A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-04 paper.tex
Minor edits

\subsection*{Applications to quantization and a relationship to factorization algebras}
\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}

@@

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CosRenorm}. 
In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re

@@

\subsubsection{Generalized Hodge theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\section{Supersymmetric Yang--Mills theories} \label{sect:SYM}

@@

\subsubsection{Holomorphic twist}
\label{sect:10dholomorphictwist}

@@

\subsubsection{Minimal twist}
\label{sect:9dminimaltwist}

@@

\subsubsection{Holomorphic twist}
\label{sect:8dholomorphictwist}

@@

\subsubsection{Topological twist}
\label{sect:8dtopologicaltwist}

@@

\subsubsection{Partially topological twist}
\label{sect:8dpartiallytopologicaltwist}

@@

\subsubsection{Minimal twist}
\label{sect:7dminimaltwist}

@@

\subsubsection{Topological twist}
\label{sect:7dtopologicaltwist}

@@

\subsubsection{Partially topological twist}
\label{sect:7dpartialtwist}

@@

\subsubsection{Holomorphic twist}
\label{sect:6dholomorphictwist}

@@

\subsubsection{Holomorphic twist}
\label{sect:6d11holomorphictwist}

@@

\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} partially topological twist}
\label{sect:6d11partialtwist}

@@

\subsubsection{Topological twist}
\label{sect:6d11topologicaltwist}

@@

\subsubsection{Minimal twist}
\label{sect:5d1minimaltwist}

@@

\subsubsection{Minimal twist}
\label{sect:5dminimaltwist}

@@

\subsubsection{Rank 2 partially topological twist}
\label{sect:5dpartialtwist}

@@

\subsubsection{Rank 2 topological twist}
\label{sect:5drank2topologicaltwist}

@@

\subsubsection{Rank 4 twist}
\label{sect:5drank4twist}

@@

\subsubsection{Holomorphic twist}
\label{sect:4d1holomorphictwist}

@@

\subsubsection{Holomorphic twist}
\label{sect:4d_2_holomorphictwist}

@@

\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
\label{sect:4d2Donaldson}

@@

\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} twist}
\label{sect:4d_2_11}

@@

\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} topological twist}
\label{sect:4d4Atwist}

@@

\subsubsection{Rank (1, 1) twist}
\label{sect:4d4partialtwist}

@@

\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} twist}

@@

\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} twist}
\label{sect:4dqgltwist}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with matter} \label{sect:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.

>>>>

\subsection*{Applications to Quantization and a Relationship to Factorization Algebras}
\addcontentsline{toc}{subsection}{Applications to quantization and a relationship to factorization algebras}

@@

To rigorously study the quantization of supersymmetric Yang-Mills theory we can work with the mathematical theory of renormalization developed by Costello in \cite{CostelloBook}. 
In the context of (non-supersymmetric) Yang-Mills theory it is shown that this theory of re

@@

\subsubsection{Generalized Hodge Theory}
Generalized BF theories can be naturally deformed to theories which are perturbatively trivial, but which arise as shadows of non-trivial non-perturbative theories.  These will often appear as topological twists of supersymmetric field theories, the most famous example being the 2d A-model \chris{refer also to the introduction}. By a deformation we will mean a $\CC[t]$-family of classical BV theories which reduce to the given theory at $t=0$.

@@

\section{Supersymmetric Yang--Mills Theories} \label{sect:SYM}

@@

\subsubsection{Holomorphic Twist}
\label{sect:10dholomorphictwist}

@@

\subsubsection{Minimal Twist}
\label{sect:9dminimaltwist}

@@

\subsubsection{Holomorphic Twist}
\label{sect:8dholomorphictwist}

@@

\subsubsection{Topological Twist}
\label{sect:8dtopologicaltwist}

@@

\subsubsection{Partially Topological Twist}
\label{sect:8dpartiallytopologicaltwist}

@@

\subsubsection{Minimal Twist}
\label{sect:7dminimaltwist}

@@

\subsubsection{Topological Twist}
\label{sect:7dtopologicaltwist}

@@

\subsubsection{Partially Topological Twist}
\label{sect:7dpartialtwist}

@@

\subsubsection{Holomorphic Twist}
\label{sect:6dholomorphictwist}

@@

\subsubsection{Holomorphic Twist}
\label{sect:6d11holomorphictwist}

@@

\subsubsection{Rank \texorpdfstring{$(1, 1)$}{(1,1)} Partially Topological Twist}
\label{sect:6d11partialtwist}

@@

\subsubsection{Topological Twist}
\label{sect:6d11topologicaltwist}

@@

\subsubsection{Minimal Twist}
\label{sect:5d1minimaltwist}

@@

\subsubsection{Minimal Twist}
\label{sect:5dminimaltwist}

@@

\subsubsection{Rank 2 Partially Topological Twist}
\label{sect:5dpartialtwist}

@@

\subsubsection{Rank 2 Topological Twist}
\label{sect:5drank2topologicaltwist}

@@

\subsubsection{Rank 4 Twist}
\label{sect:5drank4twist}

@@

\subsubsection{Holomorphic Twist}
\label{sect:4d1holomorphictwist}

@@

\subsubsection{Holomorphic Twist}
\label{sect:4d_2_holomorphictwist}

@@

\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} Topological Twist}
\label{sect:4d2Donaldson}

@@

\subsubsection{Rank \texorpdfstring{$(1,1)$}{(1,1)} Twist}
\label{sect:4d_2_11}

@@

\subsubsection{Rank \texorpdfstring{$(2,0)$}{(2,0)} Topological Twist}
\label{sect:4d4Atwist}

@@

\subsubsection{Rank (1, 1) Partially Topological Twist}
\label{sect:4d4partialtwist}

@@

\subsubsection{Rank \texorpdfstring{$(1, 2)$}{(1,2)} Topological Twist}

@@

\subsubsection{Rank \texorpdfstring{$(2, 2)$}{(2,2)} Topological Twist}
\label{sect:4dqgltwist}

@@

\subsection{\texorpdfstring{$\cN=(2,2)$}{N=(2,2)} Super Yang-Mills with Matter} \label{sect:2d(2,2)}
First, let's consider the $\mc N=(2,2)$ super Yang-Mills theory, which arises via dimensional reduction from 3d $\mc N=2$ super Yang-Mills.  This theory includes a gauge multiplet with gauge group $G$ and a chiral multiplet valued in a representation $R$ of $G$.  The R-symmetry group is $G_R = \spin(2;\CC) \times \spin(2;\CC) \iso \CC^\times \times \CC^\times$, with the factors acting by their vector representation on $W_+$ and $W_-$ repectively.
